### 2015-02-07 cav-2015-tex/evaluation.tex
changing summary to symbolic

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the summary heap with the~\gsetxt{} and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

@@

The number of states explored varies between algorithms. For example,
\gsetxt{} creates additional points of nondeterminism during field reads, 
while reference compares are completely deterministic. Thus, in
example programs with large numbers of reference compares, e.g.,
TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
exceed those for \gsetxt{}. We observed that the additional states
generated by the summary heap algorithm are unsatisfiable at the point
of reference compares; this is why they do not contribute any
additional branches in the final symbolic execution tree. Furthermore,
the larger state count does not impact the overall runtime of the
technique.

>>>>

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the symbolic heap with the~\gsetxt{} and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

@@

The number of states explored varies between algorithms. For example,
\gsetxt{} creates additional points of nondeterminism during field reads, 
while reference compares are completely deterministic. Thus, in
example programs with large numbers of reference compares, e.g.,
TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
exceed those for \gsetxt{}. We observed that the additional states
generated by the symbolic heap algorithm are unsatisfiable at the point
of reference compares; this is why they do not contribute any
additional branches in the final symbolic execution tree. Furthermore,
the larger state count does not impact the overall runtime of the
technique.

### 2015-02-07 cav-2015-tex/rw.tex
changing summary to symbolic

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic
execution with lazy initialization using on-the-fly reasoning to model
a black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by~\gsetxt{} by constructing a single summary heap
and polynomially-sized path condition for each control flow path.

>>>>

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
% Limitations of early symbolic execution techniques included non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations have sought to overcome these limitations.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.
% and fragmenting the path condition. Producing a complete path
%condition for a single given control flow path would require merging
%an exponential number of states.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization using on-the-fly reasoning to model a
black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by~\gsetxt{} by constructing a single
symbolic heap and polynomially-sized path condition for each control
flow path.
